Structured Versus Decorated Cospans

### 2020-11-26 cospans.tex
Worked on Theorems 2.1, 2.2, 2.3.

\begin{proof}
Monoidal and symmetric monoidal double categories are introduced in Definitions \ref{defn:monoidal_double_category} and \ref{defn:symmetric_monoidal_double_category}. To make $F\lCsp$ into a symmetric monoidal double category, we must show that both the category of objects $F\lCsp_0$ and the category of arrows $F\lCsp_1$ are symmetric monoidal, show that the monoidal unit of $F\lCsp_0$ is preserved by the unit functor $U$, show that the source and target functors $S,T \colon F\lCsp_1 \to F\lCsp_0$ are strict symmetric monoidal functors which preserve the associativity and unit constraints, define the globular isomorphisms $\chi$ and $\mu$ that relate how composition and units interact with the tensor product, and check that the required axioms are satisfied.

>>>>

\begin{proof}
Monoidal and symmetric monoidal double categories are introduced in Definitions \ref{defn:monoidal_double_category} and \ref{defn:symmetric_monoidal_double_category}. To make $F\lCsp$ into a symmetric monoidal double category, we must show that both the category of objects $F\lCsp_0$ and the category of arrows $F\lCsp_1$ are symmetric monoidal, show that the monoidal unit of $F\lCsp_0$ is preserved by the unit functor $U \maps F\lCsp_0 \to F\lCsp_1$, show that the source and target functors $S,T \colon F\lCsp_1 \to F\lCsp_0$ are strict symmetric monoidal, define the globular isomorphisms $\chi$ and $\mu$ that relate how composition and units interact with the tensor product, and check that the required axioms are satisfied.
